Code:
\begin{lstlisting} 
 #include <stdio.h>
 int main() {
         int numerical_var = 42;
         int *numerical_var_ptr;

         numerical_var_ptr = & numerical_var;

         printf("Address of the variable numerical_var is: %p  \n", &numerical_var);
         printf("the value stored in numerical_var_ptr is: %p  \n", numerical_var_ptr);

         printf("Value of the variable numerical_var is: %d \n", numerical_var);
         printf("value of the memory address in numerical_var is: %d \n", *numerical_var_ptr);

         return(0);
 }
\end{lstlisting}

After compiling and running the above code, the output will be something similar to:
\begin{lstlisting} 
Address of the variable numerical_var is: 0x7ffdea32e3fc
the value stored in numerical_var_ptr is: 0x7ffdea32e3fc
Value of the variable numerical_var is: 42
value of the memory address in numerical_var is: 42
\end{lstlisting}




\begin{enumerate}
    \item \textbf{Variable Declaration and Initialization (Line 1):} An integer variable is declared and initialized to the value \(42\). This variable will store an integer value.

    \item \textbf{Pointer Declaration (Line 2):} A pointer variable is declared. This pointer is intended to reference an integer value by storing the address of an integer variable.

    \item \textbf{Address Assignment (Line 4):} The address of the integer variable is assigned to the pointer using the address-of operator (\&).

    \item \textbf{Address Printing (Line 6):} The address of the integer variable is printed using the \texttt{printf} function with the \%p format specifier, which is used for pointers.

    \item \textbf{Pointer Value Printing (Line 7):} The value stored in the pointer, which is the address of the integer variable, is printed.

    \item \textbf{Variable Value Printing (Line 9):} The value of the integer variable is printed directly.

    \item \textbf{Dereferencing and Value Printing (Line 10):} The pointer is dereferenced using the asterisk (*) operator to access the value stored at the referenced address. The value is then printed.
\end{enumerate}